\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.2in,top=0.2in,bottom=0.2in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{lipsum}

% Remove page numbers
\pagestyle{empty}

% Custom section formatting
\titleformat{\section}
  {\large\bfseries}
  {}
  {0em}
  {}
  [\titlerule]

\titleformat{\subsection}
  {\normalsize\bfseries}
  {}
  {0em}
  {}

% Reduce spacing between sections and subsections by 50%
\titlespacing*{\section}{0pt}{0.5\baselineskip}{0.25\baselineskip}
\titlespacing*{\subsection}{0pt}{0.25\baselineskip}{0.125\baselineskip}

% Custom list formatting with reduced spacing
\setlist[itemize]{leftmargin=*,noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt}
\setlist[enumerate]{leftmargin=*,noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt}

% Custom spacing for entries
% Reduce paragraph spacing
\setlength{\parskip}{0.15\baselineskip}
\setlength{\parindent}{0pt}

% Reduce spacing around minipage environments
\setlength{\abovedisplayskip}{0.25\baselineskip}
\setlength{\belowdisplayskip}{0.25\baselineskip}

% Header formatting
\newcommand{\cvheader}[4]{
  \begin{center}
    {\Large\bfseries #1}\\[0.25em]
    {\normalsize #2}\\[0.15em]
    {\small #3}\\[0.15em]
    {\small #4}
  \end{center}
  \vspace{0.25em}
}

% Custom itemize for achievements
\newenvironment{achievements}
  {\begin{itemize}[leftmargin=*]}
  {\end{itemize}}

\begin{document}

% HEADER SECTION
\begin{center}
{\large\bfseries Liam Power} \hfill {\large liambotongpower@gmail.com} \hfill {\large liampower.ie}
\end{center}

\section{PROFESSIONAL SUMMARY} 

Highly motivated and results-oriented Computer Science graduate with proven experience in software engineering, AI development, and data analysis. Successfully delivered full-stack applications, architected AI pipelines, and managed projects using Agile methodologies, consistently exceeding expectations. Demonstrated ability to work effectively in teams, deliver high-quality results, and solve complex problems. Seeking a challenging role where I can leverage my technical skills and contribute to a dynamic environment. Visit liampower.ie for more.


\section{EDUCATION}

\textbf{BA (Hons) Major in Computer Science and Minor in Business} \hfill \textbf{April 2027}\\
Trinity College Dublin, Co. Dublin\\
Current Grade: I. I, First Class Honours (4.0 GPA)

\section{EXPERIENCE}

\subsection{Software Engineer, IBM \hfill January 2025 - May 2025}
\begin{itemize}
\item Architected AI-powered content generation pipeline with RAG, web search integration, and multi-LLM support via LiteLLM, increasing output quality by 45\% while reducing costs by 40\% through intelligent fallback systems.
\item Developed authentication and user history system with Firebase integration and secure API routes, enabling session recall and content re-customization capabilities, resulting in 84\% user retention rate.
\item Built full-stack React/Flask application with login/signup, article preview, podcast player, and dark/light mode, implementing comprehensive test coverage that reduced production bugs by 60\%.
\item Established CI/CD pipeline with test-gated merges and AWS deployment, executed 4 Agile sprints using Kanban methodology, adapting deliverables based on IBM stakeholder feedback.
\end{itemize}

\subsection{STEM Educator, Trinity Walton Club \hfill June 2024 - Present}
\begin{itemize}
\item Facilitate hands-on STEM learning for post-primary students at TCD collaborating with postgraduate  team to deliver interactive sessions, teaching 200+ students annually with 4.8/5 average satisfaction rating (based on classroom surveys).
\item Design and deliver interactive investigations and team challenges that cultivate critical thinking and higher-order reasoning in dynamic, non-formal learning environments, with 92\% of students reporting increased interest in STEM subjects. 
\item Contribute to club's impact of delivering more than 7,000 STEM engagements in its first decade, with approximately 145 of my 170 students (85\%) progressing to STEM degrees.
\end{itemize}

\section{PROJECTS}

\subsection{SpotPlots (TypeScript, Python)\hfill February 2025 - Present}
\begin{itemize}
\item Co-founded and developed property analysis startup through Trinity's LaunchBox incubator program, finishing in the top 5 of 2025 cohort and securing a summer residency.
\item Developed location intelligence platform with real-time transit data and property metrics filtering, helping users identify optimal locations; achieved 92\% satisfaction rate from initial user interviews.
\item Built responsive Next.js web application with MongoDB backend featuring interactive maps, personalized recommendations, and detailed scoring systems with JWT authentication.
\end{itemize}

\subsection{Sentiment-Driven Predictive Market Algorithm (JavaScript, C++) \hfill August 2025 - Present}
\begin{itemize}
\item Developed algorithmic trading system for cryptocurrency markets, achieving 18\% higher ROI than baseline strategies while implementing fractional Kelly criterion risk management that reduced maximum drawdown by 35\%.
\item Implemented quantitative framework combining market probability assessment with sentiment analysis to create adjusted probability models, improving prediction accuracy by 12\% over market consensus and improving sentiment classification to 86\%.
\item Built scalable data pipeline with Redis caching, integrating Polymarket for real-time price feeds and Reddit for sentiment extraction, processing 50,000+ social media posts daily with 99.7\% uptime and sub-100ms response times.
\end{itemize}

\subsection{Investigating Barriers to AI Adoption in Irish SMEs, Laidlaw Foundation \hfill May 2025 - September 2025}
\begin{itemize}
\item Conducted comprehensive mixed-methods research investigating why Irish small and medium enterprises lag behind larger counterparts in AI adoption, with only 25\% adoption rate compared to 40\% in large enterprises.
\item Executed semi-structured interviews with 13 Irish SME decision-makers across diverse sectors to examine real-world implementation challenges
\item Selected to present research findings at the Laidlaw Foundation Conference in October to an audience of 300 participants.
\end{itemize}

\section{ACHIEVEMENTS \& SKILLS}

\begin{minipage}[t]{0.60\textwidth}
\begin{itemize}
\item Top 3 Finish in Microsoft Security Hackathon 2025
\item Awarded the Laidlaw Leadership \& Research Scholarship (€10,000)
\item Co-founded TCD Think Tank, Ireland's first student-led think tank
\item Awarded the Sandford Park Academic Scholarship (€25,000)
\item TCD Teaching Assistant for CSU11011
\item TCD Research Assistant for Dr. James Ng
\item Computer Science and Business Student Union Representative
\item S2S Student Mentor
\end{itemize}
\end{minipage}
\hfill
\begin{minipage}[t]{0.40\textwidth}
\begin{itemize}
\item \textbf{Languages:} Python, JavaScript, Java, C++, SQL, R, HTML/CSS
\item \textbf{Frameworks:} React, Node.js, Django, Flask, Spring Boot
\item \textbf{Tools:} Git, Docker, AWS, MongoDB, PostgreSQL, Kubernetes, Jupyter
\item \textbf{Testing/Quality:} Jest, Pytest, Selenium, CI/CD, Firebase, JWT
\end{itemize}
\end{minipage}

\end{document}
